Output Summary

### 2022-04-25 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Move all output rmd sections to separate child documents

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
editor_options: 
  chunk_output_type: console
---

```{r directories, include = F}
# set root directory to the project directory: one level up from this location
knitr::opts_knit$set(root.dir = "../")
```

```{r setup, include = FALSE}
# set global knitting options
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")

# load packages
source("00-packages.R")

# load all necessary functions
invisible(sapply(list.files(path = "01-functions", pattern = "\\.R$", full.names = T), source))

# set the input directory
in_dir = "02-model/model-output"

# read information from this model
model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))

# extract the posterior samples
# post-MCMC thinning allowed to reduce run time of this document
if (params$thin_percent < 1) {
  post = post_thin(model_info$post, keep_percent = params$thin_percent)
} else {
  post = model_info$post
}

# extract the model data 
jags_data = model_info$jags_data
```

```{r dimension-ids}
# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])

# which years are "observable" for at least some quantities?
observable = 2:jags_data$ny_obs

# which years are simulated for at least some quantities?
simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))

# which years should be included in time series plots?
if (params$include_sim_years) {
  ts_yrs = c(observable, simulated)
} else {
  ts_yrs = observable
}

# which years can be plotted for SARs? Drop off last kmax years
# since brood year adult returns not complete
sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]

# population names
pops = colnames(jags_data$Ra_obs)

# origin names
origins = c("NOR", "HOR")

# dimension IDs
i_fall   = 1  # fall migrants are i = 1
i_spring = 2  # spring migrants are i = 2,
o_nor    = 1  # natural origin are o = 1,
o_hor    = 2  # hatchery origin are o = 2,
j_cat    = 1  # Catherine Creek is j = 1
j_los    = 2  # Lostine River is j = 2
j_min    = 3  # Minam River is j = 3
j_ugr    = 4  # Upper Grande Ronde River is j = 4
k_3      = 1  # age 3 is k = 1
k_4      = 2  # age 4 is k = 2
k_5      = 3  # age 5 is k = 3

# ko represents "age/origin" combo
# e.g., ko = 1 is age 3 NORs
# e.g., ko = 5 is age 4 HORs
# these objects specify which elements of ko are for different aggregations of these
ko_age = list(
  ko_3 = c(1, 4),
  ko_4 = c(2, 5),
  ko_5 = c(3, 6)
)

ko_origin = list(
  ko_nor = 1:3,
  ko_hor = 4:6
)

# make the labels for which elements of the rho matrices contain unique elements
dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
vcov_cols = dummy_cols[lower.tri(dummy_cols)]
vcov_rows = dummy_rows[lower.tri(dummy_rows)]
vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
```

# MCMC Information {.tabset .tabset-pills}

## Time Information

```{r mcmc-time-info}
# Calculate hours per 10,000 iterations
hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
  # calculation of total iters differs if parallel or not
  if (parallel) {
    total_iters = n_adapt + n_post + n_burn
  } else {
    total_iters = (n_adapt + n_post + n_burn) * n_chains
  }
  ten_thousands_of_total_iters = total_iters/10000

  # calculate hours elapsed
  time_diff = as.POSIXct.default(model_info$jags_time["stoptime"]) - as.POSIXct.default(model_info$jags_time["starttime"])
  time_number = as.numeric(time_diff)
  time_units = attributes(time_diff)$units
  hour_convert = switch(time_units,
                        "secs" = 3600,
                        "mins" = 60,
                        "hours" = 1,
                        "days" = 1/24)
  hours_diff = time_number/hour_convert

  # calculate/round rate
  round(hours_diff/ten_thousands_of_total_iters, 2)
})

# combine relevant info into a data frame
df = data.frame(Value = c(model_info$jags_time, ifelse(model_info$jags_dims$parallel, "Yes", "No"), hrs_per_ten_thousand_iters))
rownames(df) = c("Time Started", "Time Ended", "Time Elapsed", "Chains Ran in Parallel?", "Hours Per 10,000 Iterations")

# make a kable for printing in output
kable(df) %>%
  kable_styling(full_width = F, bootstrap_options = "condensed") %>%
  column_spec(1, bold = TRUE)
```

## Attributes

This table shows some dimensions of the MCMC run.

```{r mcmc-dims}
# query the dimensions of the posterior samples
dims = post_dim(post)

# build a data frame for printing
df = data.frame(Quantity = c("Burn-in + Adapt Iters", "Post Burn-in Iters", "Thinning Interval", "Chains", "Saved Iters", "Monitored Quantities"), Value = unname(dims))

# render the table
kable(df, format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = F, bootstrap_options = c("striped", "condensed")) %>%
  column_spec(1, bold = TRUE)
```

## Sampling Diagnostics {.tabset .tabset-pills}

@@

### Summary Table

@@

### Figures {.tabset .tabset-pills}

@@

#### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}

##### Distribution

@@

##### Least Converged

@@

#### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}

##### Distribution

@@

#### $\hat{R} > 1.1$ {.tabset .tabset-pills}

##### Distribution

@@

## WAIC

WAIC is a measure of model parsimony. The quantity `pD` is an index of model complexity (i.e., "effective parameters") and `deviance` is an index of model fit to the data. There are two methods of calculating `pD`, both are shown below. As for other measures like AIC or BIC, these numbers are really only relevant for comparing among models fitted to the same data set.

```{r calculate-waic, eval = model_info$do_lppd}
summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
  # calculate total lppd summed across all data sets within a given year
  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))

  tmp_log = log(apply(exp(total_lppd), 2, mean))
  tmp_sum = -2 * sum(tmp_log)

  pD1 = 2 * sum(tmp_log - apply(total_lppd, 2, mean))
  pD2 = sum(apply(total_lppd, 2, var))
  round(c(deviance = tmp_sum, pD1 = pD1, pD2 = pD2, WAIC1 = tmp_sum + 2 * pD1, WAIC2 = tmp_sum + 2 * pD2))
}

waic_out = summarize_lppd("_lppd[year,.+]$")

waic_out = as.data.frame(as.list(waic_out))
waic_out %>%
  kbl(format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
```

```{r dont-calculate-waic, eval = !model_info$do_lppd, results='asis'}
cat("_Calculation of log posterior predictive density values needed to calculate WAIC was toggled off when fitting this model, so this output is omitted._")
```

## Posterior Predictive Checks

This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model. For each observed data point and MCMC iteration, a value was simulated from the model. The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated. P-values close the 0.5 are ideal (0.4 -- 0.6 have no color below), values closer to 1 (red below) indicate over-dispersion (i.e., model fits real data worse than expected), and values closer to 0 (blue below) indicate under-dispersion (i.e., model fits real data better than expected). Across years within a data set, p-values were summarized as the median and central 95% intervals. The left two columns show the percent of years that had extreme p-values, providing another indication of how often the model fit the real data far better (<0.05) or worse (>0.95) than expected.

The fit criterion differed depending on the likelihood function used to fit the model to the data set:

* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation. This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities. This applies to all composition data, the survival from BON to LGR data, and the pre-spawn survival data.

```{r calculate-bayesian-pvals, eval = model_info$do_pp_check}
# function to summarize bayesian p-values within a data source
summarize_bp = function(bp) {
  data.frame(
    "N" = apply(bp, 2, function(x) sum(!is.na(x))),
    "median" = apply(bp, 2, median, na.rm = TRUE),
    "q2.5" = apply(bp, 2, function(x) quantile(x, 0.025, na.rm = TRUE)),
    "q97.5" = apply(bp, 2, function(x) quantile(x, 0.975, na.rm = TRUE)),
    "p_lt_0.05" = apply(bp, 2, function(x) sum(x < 0.05 & !is.na(x))/sum(!is.na(x))),
    "p_gt_0.95" = apply(bp, 2, function(x) sum(x > 0.95 & !is.na(x))/sum(!is.na(x)))
  )
}

### CALCULATE BAYESIAN P-VALUES: ABUNDANCE DATA SOURCES ###

# fall trap
new = post_subset(post, "Pa_obs_new_dev", TRUE)
obs = post_subset(post, "Pa_obs_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], "fall-mig", pops)
bp = bp[,"fall-mig",]
Pa_bp = data.frame(
  name = rep("Juveniles", 4), pop = pops,
  origin = rep("NOR", 4), LH_type = rep("Fall Migrants", 4),
  summarize_bp(bp)
)
rownames(Pa_bp) = NULL

# spring trap
new = post_subset(post, "^Mb_obs_new_dev", TRUE)
obs = post_subset(post, "^Mb_obs_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), "NOR", pops)
bp = bp[,"spring-mig","NOR",]
Mb_bp = data.frame(
  name = rep("Juveniles", 4), pop = pops,
  origin = rep("NOR", 4), LH_type = rep("Spring Migrants", 4),
  summarize_bp(bp)
)
rownames(Mb_bp) = NULL

# adult abundance
new = post_subset(post, "Ra_obs_new_dev", TRUE)
obs = post_subset(post, "Ra_obs_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
Ra_bp = data.frame(
  name = rep("Adults", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(Ra_bp) = NULL

### CALCULATE BAYESIAN P-VALUES: SURVIVAL DATA SOURCES ###

# summer tagging survival
new = post_subset(post, "Lphi_obs_new_Pb_Ma_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Pb_Ma_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
phi_Pb_Ma_bp = data.frame(
  name = rep("Summer Tagging to LGR", 4), pop = pops,
  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(phi_Pb_Ma_bp) = NULL

# fall & winter trap survival
new = post_subset(post, "Lphi_obs_new_Pa_Ma_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Pa_Ma_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), pops)
bp = cbind(CAT_fall = bp[,"fall-mig","CAT"], CAT_spring = bp[,"spring-mig","CAT"],
           LOS_fall = bp[,"fall-mig","LOS"], LOS_spring = bp[,"spring-mig","LOS"],
           MIN_fall = bp[,"fall-mig","MIN"], MIN_spring = bp[,"spring-mig","MIN"],
           UGR_fall = bp[,"fall-mig","UGR"], UGR_spring = bp[,"spring-mig","UGR"])
phi_Pa_Ma_bp = data.frame(
  name = rep(c("Fall Trap to LGR", "Winter Tagging"), each = 4), pop = rep(pops, 2),
  origin = rep("NOR", 8),   LH_type = rep(c("Fall Migrants", "Spring Migrants"), each = 4),
  summarize_bp(bp)
)
rownames(phi_Pa_Ma_bp) = NULL

# trib to lgr survival
new = post_subset(post, "Lphi_obs_new_Mb_Ma_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Mb_Ma_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), origins, pops)
bp = bp[,"spring-mig",,]
bp = cbind(CAT_NOR = bp[,"NOR","CAT"], CAT_HOR = bp[,"HOR","CAT"],
           LOS_NOR = bp[,"NOR","LOS"], LOS_HOR = bp[,"HOR","LOS"],
           MIN_NOR = bp[,"NOR","MIN"], MIN_HOR = bp[,"HOR","MIN"],
           UGR_NOR = bp[,"NOR","UGR"], UGR_HOR = bp[,"HOR","UGR"])
phi_Mb_Ma_bp = data.frame(
  name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
  origin = rep(origins, 4), LH_type = rep("Spring Migrants", 8),
  summarize_bp(bp)
)
rownames(phi_Mb_Ma_bp) = NULL

# hydropower survival
new = post_subset(post, "Lphi_obs_new_Ma_O0_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Ma_O0_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
phi_Ma_O0_bp = data.frame(
  name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
  origin = origins, LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(phi_Ma_O0_bp) = NULL

### CALCULATE BAYESIAN P-VALUES: LENGTH DATA SOURCES ###

# summer length
new = post_subset(post, "L_Pb_obs_new_dev", TRUE)
obs = post_subset(post, "L_Pb_obs_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
L_Pb_bp = data.frame(
  name = rep("Summer Length", 4), pop = pops,
  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(L_Pb_bp) = NULL

# spring length
new = post_subset(post, "L_Mb_obs_new_dev", TRUE)
obs = post_subset(post, "L_Mb_obs_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
L_Mb_bp = data.frame(
  name = rep("Spring Length", 4), pop = pops,
  origin = rep("NOR", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(L_Mb_bp) = NULL

### CALCULATE BAYESIAN P-VALUES: COMPOSITION DATA SOURCES ###

# weir composition
new = post_subset(post, "x_Ra_new_dev", TRUE)
obs = post_subset(post, "x_Ra_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
bp[jags_data$nx_Ra == 0 | is.na(jags_data$nx_Ra)] = NA
x_Ra_bp = data.frame(
  name = rep("Weir", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(x_Ra_bp) = NULL

# carcass composition
new = post_subset(post, "x_Sa_prime_new_dev", TRUE)
obs = post_subset(post, "x_Sa_prime_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
bp[jags_data$nx_Sa_prime == 0 | is.na(jags_data$nx_Sa_prime)] = NA
x_Sa_prime_bp = data.frame(
  name = rep("Carcasses", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(x_Sa_prime_bp) = NULL

# pre-spawn survival
new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
x_carcass_spawned_bp = data.frame(
  name = rep("Prespawn", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(x_carcass_spawned_bp) = NULL

# movement survival from BON to LGR
new = post_subset(post, "x_LGR_new_dev", TRUE)
obs = post_subset(post, "x_LGR_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
x_LGR_bp = data.frame(
  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
  origin = origins, LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(x_LGR_bp) = NULL

### COMBINE INTO ONE TABLE ###
bp_tab = rbind(
  Pa_bp, Mb_bp, Ra_bp,
  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
)

# add a main data category variable
category = rep(NA, nrow(bp_tab))
category = ifelse(bp_tab$name %in% c("Adults", "Juveniles"), "Abundance", category)
category = ifelse(bp_tab$name %in% c("Weir", "Carcasses"), "Composition", category)
category = ifelse(bp_tab$name %in% c("Summer Length", "Spring Length"), "Mean Length", category)
category[is.na(category)] = "Survival"
bp_tab = data.frame(category = category, bp_tab)

# drop the several cases with no data
# MIN HOR survival to LGR and MIN weir data
bp_tab = bp_tab[bp_tab$N > 0,]

# re-order output/misc formatting
bp_tab = bp_tab[order(bp_tab$category, bp_tab$name, bp_tab$pop, bp_tab$origin),]
bp_tab = bp_tab[,c("category", "name", "pop", "LH_type", "origin", "N", "median", "q2.5", "q97.5", "p_lt_0.05", "p_gt_0.95")]
bp_tab$p_lt_0.05 = paste0(round(bp_tab$p_lt_0.05 * 100), "%")
bp_tab$p_gt_0.95 = paste0(round(bp_tab$p_gt_0.95 * 100), "%")
rownames(bp_tab) = NULL
```

```{r bayesian-pvals-table, eval = model_info$do_pp_check}
# a function to color cells depending on the value
assign_color = function(x) {
  red_pal = colorRampPalette(c("white", "red"))
  blue_pal = colorRampPalette(c("blue", "white"))
  red_cols = red_pal(5)
  blue_cols = blue_pal(5)
  cols = c(blue_cols, red_cols)
  bin_names = levels(cut(rbeta(1e6, 1, 1), breaks = seq(0,1,0.1), include.lowest = TRUE))
  names(cols) = bin_names
  bins = cut(x, breaks = seq(0,1,0.1), include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  alpha(unname(cols_use), 0.5)
}

# produce the kable
bp_tab %>%
  kbl(digits = 2, col.names = c("Class", "Lifestage", "Population", "Migratory Type", "Origin", "Years w/Data", "Median", "2.5%", "97.5%", "<0.05", ">0.95"),
      align = c("lllllcccccc")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
  add_header_above(c("Data Type Information" = 5, "P-value Summaries" = 4, "% of Extreme P-values" = 2)) %>%
  column_spec(7, background = assign_color(bp_tab[,7])) %>%
  column_spec(8, background = assign_color(bp_tab[,8])) %>%
  column_spec(9, background = assign_color(bp_tab[,9])) %>%
  collapse_rows(1:5) 
```

```{r dont-calculate-bayesian-pvals, eval = !model_info$do_pp_check, results='asis'}
cat("_Generation of simulated data that can be compared to the observed data in terms of model fit was toggled off when fitting this model, so this output is omitted._")
```

# Fit to Data

In all figures below, the thick red line is the posterior median value each year, the red region is the equal-tailed 95% credible interval, and blue points are "observed" data (estimated from raw data external to the model).

## Abundance Data {.tabset .tabset-pills}

### Fall Parr Abundance

```{r fall-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Pa[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Pa_obs[observable,i_fall,j]), jags_data$sig_Pa_obs[observable,i_fall,j]),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Fall Parr Abundance")
```

### Spring Smolt Abundance

```{r spring-trap-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Mb[year,LH_type,origin,pop]$", year = ts_yrs, origin = o_nor, LH_type = i_spring, pop = j)), 
               get_obs_ests_log_normal(log(jags_data$Mb_obs[observable,i_spring,o_nor,j]), jags_data$sig_Mb_obs[observable,i_spring,o_nor,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Spring Smolt Abundance")
```

### Adult Return Abundance

```{r adult-N-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Ra_tot[year,pop]$", year = ts_yrs, pop = j)),
               get_obs_ests_log_normal(log(jags_data$Ra_obs[observable,j]), jags_data$sig_Ra_obs[observable,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Adult Return Abundance")
```

## Survival Data {.tabset .tabset-pills}

### Summer Parr $\rightarrow$ LGR

```{r summer-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pb_Ma[year,pop]", year = ts_yrs, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pb_Ma[observable,j], jags_data$sig_Lphi_obs_Pb_Ma[observable,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Summer\\,Parr \\rightarrow LGR\\,Survival$"))
```

### Fall Parr $\rightarrow$ LGR

```{r fall-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_fall,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_fall,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Fall\\,Parr \\rightarrow LGR\\,Survival$"))
```

### Winter Parr $\rightarrow$ LGR

```{r winter-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
```

### Spring Smolt $\rightarrow$ LGR (NOR)

```{r spring-surv-fit-nor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_nor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_nor,j]),
               main = pops[j], yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(NOR)$"))
```

### Spring Smolt $\rightarrow$ LGR (HOR)

```{r spring-surv-fit-hor, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]$", year = ts_yrs, LH_type = i_spring, origin = o_hor, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j], jags_data$sig_Lphi_obs_Mb_Ma[observable,i_spring,o_hor,j]),
               main = pops[j], yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Spring\\,Smolt \\rightarrow LGR\\,Survival\\,(HOR)"))
```

### LGR Smolt $\rightarrow O_0$ (NOR)

```{r hydro-nor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_nor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_nor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

### LGR Smolt $\rightarrow O_0$ (HOR)

```{r hydro-hor-surv-fit, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Ma_O0[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_logit_normal(jags_data$Lphi_obs_Ma_O0[observable,o_hor], jags_data$sig_Lphi_obs_Ma_O0[observable,o_hor]),
             main = TeX("$LGR\\,Smolt \\rightarrow O_0\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

### BON Adults $\rightarrow$ LGR (NOR)

```{r BON-LGR-surv-fit-nor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_nor)),
             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_nor], jags_data$x_BON[observable,o_nor] - jags_data$x_LGR[observable,o_nor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(NOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

### BON Adults $\rightarrow$ LGR (HOR)

```{r BON-LGR-surv-fit-hor, fig.width = 6, fig.height = 5}
par(oma = c(1.5,1.5,0,0), mfrow = c(1,1))
plot_tseries(post_summ(post, sub_index("^phi_Rb_Ra[year,origin]$", year = ts_yrs, origin = o_hor)),
             get_obs_ests_multinomial(cbind(jags_data$x_LGR[observable,o_hor], jags_data$x_BON[observable,o_hor] - jags_data$x_LGR[observable,o_hor]), 1),
             main = TeX("$BON\\,Adults \\rightarrow LGR\\,Survival\\,(HOR)"),
             yrs = all_yrs[ts_yrs])
mtext(side = 1, outer = T, line = 0.25, "Return Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

## Composition Data {.tabset .tabset-pills .tabset-fade}

```{r calculate-aggregated-comps-model}
# extract the full posteriors of the two composition sets
p_Ra_full = post_subset(post, "p_Ra", matrix = TRUE)
p_Sa_prime_full = post_subset(post, "p_Sa", matrix = TRUE)

# primary containers: will store final recalculated output
p_Ra_age = p_Sa_prime_age = p_Ra_origin = p_Sa_prime_origin = NULL

# number of posterior samples
n = post_dim(post, "saved")

# loop through posterior samples, calculate various aggregates of composition by type
for (i in 1:n) {

  # format the posterior draw as arrays -- easier to subset
  p_Ra = array_format(p_Ra_full[i,])
  p_Sa_prime = array_format(p_Sa_prime_full[i,])

  ## BY AGE, AGGREGATED ACROSS ORIGINS

  # containers
  p_Ra_age_tmp = p_Sa_prime_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
  inds_1_age = inds_2_age = inds_3_age = p_Ra_age_tmp
  for (j in 1:jags_data$nj) {
    for (k in 1:jags_data$nk) {
      # calculate aggregate proportions for each age
      p_Ra_age_tmp[,k,j] = rowSums(p_Ra[,ko_age[[k]],j])
      p_Sa_prime_age_tmp[,k,j] = rowSums(p_Sa_prime[,ko_age[[k]],j])

      # build the element identifiers - for building names later
      inds_1_age[,k,j] = 1:jags_data$ny
      inds_2_age[,k,j] = k
      inds_3_age[,k,j] = j
    }
  }

  # vectorize, add names, and remove NAs
  p_Ra_age_v = as.numeric(p_Ra_age_tmp)
  p_Sa_prime_age_v = as.numeric(p_Sa_prime_age_tmp)
  names(p_Ra_age_v) = paste0("p_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  names(p_Sa_prime_age_v) = paste0("p_Sa_prime_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  p_Ra_age_v = p_Ra_age_v[!is.na(p_Ra_age_v)]
  p_Sa_prime_age_v = p_Sa_prime_age_v[!is.na(p_Sa_prime_age_v)]

  ## BY ORIGIN, AGGREGATED ACROSS AGES

>>>>

# MCMC Diagnostics {.tabset .tabset-pills}

@@

## Summary Table

@@

## Figures {.tabset .tabset-pills}

@@

### $1 < \hat{R} < 1.05$ {.tabset .tabset-pills}

#### Distribution

@@

#### Least Converged

@@

### $1.05 < \hat{R} < 1.1$ {.tabset .tabset-pills}

#### Distribution

@@

### $\hat{R} > 1.1$ {.tabset .tabset-pills}

#### Distribution

@@
